\documentclass[11pt,letterpaper]{article}

\usepackage[top=0.4in,bottom=0.4in,left=0.55in,right=0.55in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{lmodern}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\pagestyle{empty}
\setlength{\parindent}{0pt}

\titleformat{\section}{\large\scshape}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{3pt}{1pt}

\setlist[itemize]{leftmargin=*, itemsep=1pt, topsep=1pt, parsep=0pt}
\setlist[itemize,2]{leftmargin=12pt, itemsep=0pt, topsep=0pt, label=\textopenbullet}

\hypersetup{
  colorlinks=true,
  urlcolor=black,
  pdftitle={Bibekpreet Singh Chugh -- Resume},
  pdfauthor={Bibekpreet Singh Chugh}
}

\begin{document}

\begin{center}
{\LARGE\textbf{Bibekpreet Singh Chugh}}\\[4pt]
+91 9027844360 \textbar{} \href{mailto:hello@bsingh.codes}{hello@bsingh.codes} \textbar{} \href{https://www.linkedin.com/in/bibekpreet-singh-chugh-0b3a96325/}{LinkedIn} \textbar{} \href{https://github.com/BSinghOP}{GitHub} \textbar{} \href{https://bsingh.codes}{Portfolio}
\end{center}

\section*{Summary}
Computer Science undergraduate at SRM Delhi-NCR with hands-on experience in full-stack web development, DevOps, and production game-server infrastructure. Build full-stack applications with React, Node.js, and MySQL deployed on Linux VPS behind Nginx and PM2. Operate a production Minecraft network on Debian using Pterodactyl + Wings with a load-balanced proxy fleet and Cloudflare Spectrum DDoS mitigation, sustaining 1000+ concurrent player peaks. Active in-game server admin and Java plugin developer at Battle Pie.

\section*{Education}
\begin{itemize}
\item \textbf{SRM Institute of Science and Technology} \hfill Delhi-NCR, IN \\
B.Tech in Computer Science Engineering; \textbf{CGPA: 8.63} \hfill Aug 2024 -- Jul 2028
\item \textbf{The Adhyyan School} \hfill IN \\
Senior Secondary (CBSE), PCM: 67\% \hfill Aug 2022 -- Jul 2024
\end{itemize}

\section*{Experience}
\begin{itemize}
\item \textbf{Battle Pie -- Self-Operated Minecraft Network} \hfill IN \\
\textit{Server Admin, Plugin Developer \& Infrastructure Operator} \hfill 2023 -- Present
\begin{itemize}
\item Operate production Minecraft network with \textbf{1000+ concurrent player peaks} across a dedicated bare-metal \textbf{Debian} host fleet.
\item Orchestrate containerized game-server instances via \textbf{Pterodactyl panel with the Wings daemon}; provision lobby and gamemode servers across the host pool.
\item Front the network with a \textbf{load-balanced proxy fleet} that fans connections out to backend servers; \textbf{Cloudflare Spectrum} for L4 DDoS mitigation and SSL.
\item Develop custom \textbf{Java plugins} for backend gameplay; serve as in-game admin handling moderation, gameplay tuning, and live ops; operate the customer-facing store at \href{https://store.battlepie.net}{store.battlepie.net}.
\end{itemize}
\end{itemize}

\section*{Projects}
\begin{itemize}
\item \textbf{BSingh's Vault -- Full-Stack Bank Management System} \hfill 2025 \\
\href{https://dbms.bsingh.codes}{dbms.bsingh.codes} \textbar{} \href{https://github.com/BSinghOP/bank-management-system}{GitHub}
\begin{itemize}
\item Took DBMS course project from broken state to production-grade deployment: authentication with freeze enforcement, full transaction history, and admin panel.
\item Built with \textbf{React, Node.js, Express, MySQL}; deployed on Linux VPS behind Nginx with PM2 process supervision; sustains 99.9\% production uptime.
\end{itemize}

\item \textbf{AyuTrace -- Blockchain Herb Traceability} (Team Contributor) \hfill 2025 \\
\href{https://ethicons.vercel.app}{ethicons.vercel.app} \textbar{} \href{https://github.com/BSinghOP/ethicons-ayutrace}{GitHub}
\begin{itemize}
\item Contributed to \textbf{Solidity} smart contracts on EVM for tamper-proof Ayurvedic herb supply-chain tracking.
\item Implemented geo-tagged origin records, immutable quality certifications, and consumer-facing QR codes for full farm-to-formulation history.
\item Stack: \textbf{Next.js, Solidity, ethers.js, MongoDB}.
\end{itemize}

\item \textbf{FNDP -- AI-Powered Fake News Detector} (Team Contributor) \hfill 2025 \\
\href{https://fndp-frontend.vercel.app}{fndp-frontend.vercel.app} \textbar{} \href{https://github.com/Nikunjmiglani/FNDP---Fake-new-detector-project}{GitHub}
\begin{itemize}
\item Contributed to ML-based misinformation detection using a \textbf{Python} classification model that identifies fake headlines and articles.
\item Built \textbf{React} frontend deployed on Vercel that interfaces with the detection backend.
\end{itemize}
\end{itemize}

\section*{Achievements}
\begin{itemize}
\item \textbf{Smart India Hackathon 2025}: Cleared Internal SIH 2025 with team Ethicons (AyuTrace -- blockchain herb traceability).
\item \textbf{Hackstasy Hackathon}: Top 20 teams of 300+ participants for a scalable full-stack project.
\item \textbf{1st Prize -- College Science Project Expo}, SRM Institute of Science and Technology, Delhi-NCR.
\end{itemize}

\enlargethispage{15pt}
\section*{Technical Skills}
\begin{itemize}
\item \textbf{Languages}: C, C++, Python, Java, JavaScript, TypeScript, SQL
\item \textbf{Frameworks \& Databases}: React, Next.js, Node.js, Express, Tailwind CSS, MySQL, MongoDB
\item \textbf{Infrastructure \& DevOps}: Debian, Pterodactyl + Wings, Nginx, PM2, Cloudflare, SSL/TLS, DDoS Mitigation, GitHub Actions, Git, Vercel
\end{itemize}

\end{document}
